Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-22 doc/mc-paper.tex
Describe soundness, not completeness

Computing many useful properties of Boolean formulas, such as their weighted or unweighted model count,
is intractable on general representations. It can become tractable when formulas are expressed in a
special form, such as a deterministic,
  decomposable, negation normal form (d-DNNF) graph.
\emph{Knowledge compilation} is the process of converting a formula
into such a form. Existing knowledge compilers provide no guarantee that their output correctly
represents the original formula, and therefore they cannot validate the model counts.

@@

This paper introduces \emph{Partitioned-Operation Graphs} (POGs),
a generalization of the representations produced by current knowledge
compilers. To capture both the structure of a POG
and a checkable proof of its logical equivalence to a Boolean formula in
conjunctive normal form (CNF), we propose the CPOG (for ``checkable'' POG) file format. A CPOG
proof consists of a sequence of clause addition and deletion steps,
based on an extended resolution proof system~\cite{Tseitin:1983}.
We establish a set of conditions that a CPOG file must satisfy in order to
encode a well-formed POG and provide a valid equivalence proof.

>>>>

Computing many useful properties of Boolean formulas, such as their weighted or unweighted model count,
is intractable on general representations. It can become tractable when formulas are expressed in a
special form, such as the deterministic,
decomposable, negation normal form (d-DNNF)\@.
\emph{Knowledge compilation} is the process of converting a formula
into such a form. Existing knowledge compilers provide no guarantee that their output correctly
represents the original formula, and therefore they cannot validate the model counts.

@@

This paper introduces \emph{Partitioned-Operation Graphs} (POGs),
a generalization of the representations produced by current knowledge
compilers. The CPOG (for ``checkable'' POG) file format then
captures both the structure of a POG
and a checkable proof of its logical equivalence to a Boolean formula in
conjunctive normal form (CNF).  A CPOG
proof consists of a sequence of clause addition and deletion steps,
based on an extended resolution proof system~\cite{Tseitin:1983}.
We establish a set of conditions that, when satisified by a CPOG file, guarantee that it
encodes a well-formed POG and provides a valid equivalence proof.
